---
title: "Interesting Forecasting Applications with R"
author: "Dürdane Karabacak - IE360 - Srping 2020"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="html_document")
```


1. [Time series forecasting using ARIMA models](https://blogs.oracle.com/datascience/introduction-to-forecasting-with-arima-in-r)

    This example is important because it introduces the forecasting methodology using ARIMA models in R. 
    

2. [Using R for Time Series Analysis](https://a-little-book-of-r-for-time-series.readthedocs.io/en/latest/src/timeseries.html)

    In this page, there is an analysis for Age of Death of Successive Kings of England in R
    

3. [Forecasting with R Notes](https://kourentzes.com/forecasting/wp-content/uploads/2016/06/Forecasting-with-R-notes.pdf)

    In this pdf, there is a totalitarian teaching for forecsting, time series analysis.


4. [Forecating using multiple models](https://cran.rstudio.com/web/packages/sweep/vignettes/SW02_Forecasting_Multiple_Models.html)

    Here,  there is an example of forecasting of Gasoline pricing using three models (ARIMA, ETS, BATS)  


5. [Forecast double seasonal time series with multiple linear regression in
R](https://petolau.github.io/Forecast-double-seasonal-time-series-with-multiple-linear-regression-in-R/)

    This example shows how to forecast double seasonal time series data with multiple linear regression in R